---
output: rmarkdown::github_document
---
```{r, echo = FALSE}
knitr::opts_chunk$set(collapse=TRUE, comment="##", fig.retina=2, fig.path = "README_figs/README-")
```

## ewenthemes: Beautiful Themes and Theme Components for 'ggplot2'

[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/0.1.0/active.svg)](http://www.repostatus.org/#active)
[![Travis-CI Build Status](https://travis-ci.org/ewenme/ewenthemes.svg?branch=master)](https://travis-ci.org/ewenme/ewenthemes)

----

This is a very focused package that provides typography-centric themes and theme components for ggplot2. The core theme: `theme_ewen` uses Arial Narrow which should be installed on practically any modern system, so it's "free"-ish.

The following functions are implemented/objects are exported:

Core themes & scales:

- `theme_ewen`: Arial Narrow-based theme
- `theme_ewen_ws`: Work Sans-based theme
- `theme_ipsum_sp`: Spectral-based theme
- `scale_color_ipsum` / `scale_fill_ipsum` / `ipsum_pal`: A muted discrete color palette with 9 colors

Utilities:

- `update_geom_font_defaults`:	Update font defaults for text geoms (the default is — unsurprisingly — Arial Narrow)

The following global variables are now in your namespace:

- `font_an`: a short global alias for "`Arial Narrow`"
- `font_ws`: a short global alias for "`Work Sans`"
- `font_ws_light`: a short global alias for "`Work Sans Light`"
- `font_ws_bold`: a short global alias for "`Work Sans Bold`"
- `font_sp`: a short global alias for "`Spectral`"
- `font_sp_light`: a short global alias for "`Spectral Light`"
- `font_sp_bold`: a short global alias for "`Spectral Bold`"


### Installation

```{r eval=FALSE}
devtools::install_github("ewenme/ewenthemes")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(ewenthemes)
library(gcookbook)
library(tidyverse)

# current verison
packageVersion("ewenthemes")
```

### Base theme (Arial Narrow)

```{r fig.retina=2}
ggplot(mtcars, aes(mpg, wt)) +
  geom_point() +
  labs(x="Fuel efficiency (mpg)", y="Weight (tons)",
       title="Seminal ggplot2 scatterplot example",
       subtitle="A plot that is only useful for demonstration purposes",
       caption="Brought to you by the letter 'g'") + 
  theme_ewen()
```

### Work Sans

```{r fig.retina=2}
ggplot(mtcars, aes(mpg, wt)) +
  geom_point() +
  labs(x="Fuel efficiency (mpg)", y="Weight (tons)",
       title="Seminal ggplot2 scatterplot example",
       subtitle="A plot that is only useful for demonstration purposes",
       caption="Brought to you by the letter 'g'") + 
  theme_ewen_ws()
```

### Spectral

```{r fig.width=10, fig.height=7, fig.retina=2}
ggplot(mpg, aes(displ, hwy)) +
  geom_jitter(aes(color=class, fill=class), size=3, shape=21, alpha=1/2) +
  scale_x_continuous(expand=c(0,0), limits=c(1, 8), breaks=1:8) +
  scale_y_continuous(expand=c(0,0), limits=c(10, 50)) +
  scale_color_ipsum() +
  scale_fill_ipsum() +
  facet_wrap(~class, scales="free") +
  labs(
    title="Spectral Test",
    subtitle="This is a subtitle to see the how it looks in Spectral",
    caption="Source: ewenthemes"
  ) +
  theme_ewen_sp(grid="XY", axis="xy") +
  theme(legend.position="none") -> gg

```


### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

